Visualizing Project Evolution Through Abstract Syntax Tree Analysis

### 2016-06-27 paper/document.tex
Last change before major rehaul of intro.

The major downside to using ASTs over a method like line count is that ASTs are more expensive to compute. Our experiments were run on a Intel i7 with 16GB of RAM and an SSD. Calculating the AST diffs varied from an hour or two for smaller projects to a couple of days for very large projects. For example ANTLR4 took about 8 hours while Apache BookKeeper only took a couple of hours. The good news for ongoing projects is that AST diffs only need to be computed for new commits; TypeV can resume calculating diffs and augmenting statistics at any time. New diffs can be appended to the already existing database of previous AST diffs.

@@

One issue with analyzing individual authors is that authors can commit from a variety of different computers which can have different emails and usernames attached to their Git configuration. This may result in one author appearing as several different authors in the \texttt{git log}. There is no perfect way to deal with this problem; however, we allow the user of our software to select and view multiple authors at a time, thus allowing the user to view changes from an individual or group of developers.

@@

@@

>>>>

The major downside of AST diffs over a method like line count is that ASTs are more expensive to compute. Our experiments were run on a Intel i7 with 16GB of RAM and an SSD. Calculating the AST diffs varied from an hour or two for smaller projects to a couple of days for very large projects. For example ANTLR4 took about 8 hours while Apache BookKeeper only took a couple of hours. The good news for ongoing projects is that AST diffs only need to be computed for new commits; TypeV can resume calculating diffs and augment statistics at any time.

@@

One issue with analyzing individual authors is that authors can commit from a variety of different computers which can have different emails and usernames attached to their Git configuration. This may result in one author appearing as several different authors in the \texttt{git log}. There is no perfect way to deal with this problem; however, we added an interface for managing authors. A user can manually specify an author's various aliases using a simple dropdown list. All statistics attributed to an author's various aliases are then remapped as belonging to one canonical author as specified by the user.

In addition, our author managing view also provides a facility for selecting and deselecting authors in the view. Thus, visualization users can focus on the changes made by one author or a group of authors, rather than only having the option of view changes made by all authors cumulatively.

@@

% TODO: Add design decisions for author merging?

@@

In addition, the author statistics given in Table~\ref{tab:project-summary} was calculated after manual author merging. We are not personally familiar with the project, let alone the authors collaborating on the project. Therefore, our efforts to manually merge authors may have been erroneous.
